### 2020-06-04 writeup/intro.tex
wip

\begin{figure}[!t]
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
		\vspace{-0.075in}
		\caption{Task similarity}
		\label{fig_model_shift}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
		\vspace{-0.075in}
		\caption{Sample size}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
		\vspace{-0.075in}
		\caption{Covariate shift}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	We observe that MTL performance
	(a) undergoes transition from positive to negative transfer as \textit{task model distance} increases (Prop.\;\ref{prop_dist_transition});
	(b) undergoes transition from positive to negative transfer as source/target \text{sample size} increases (Prop.\;\ref{prop_data_size});
	(c) gets worse as \textit{covariate shift} gets more severe (larger $\lambda$) and source/target \textit{sample size} increases (Prop.\;\ref{prop_covariate}).
	The $y$-axis measures the loss of STL minus MTL.}
	\label{fig_model_shift_phasetrans}
	\vspace{-0.1in}
\end{figure}

%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.

>>>>

\begin{figure}[!t]
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/model_shift_phase_transition.pdf}
		\vspace{-0.075in}
		\caption{Task similarity}
		\label{fig_model_shift}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/datapoints_phase_transition.pdf}
		\vspace{-0.075in}
		\caption{Sample size}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.32\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/complementary.pdf}
		\vspace{-0.075in}
		\caption{Covariate shift}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	We observe that MTL performance
	(a) transitions from positive to negative transfer as \textit{task model distance} increases (Prop.\;\ref{prop_dist_transition});
	(b) transitions from positive to negative transfer as source/target \text{sample size} increases (Prop.\;\ref{prop_data_size});
	(c) worsens as \textit{covariate shift} gets more severe (larger $\lambda$) and source/target \textit{sample size} increases (Prop.\;\ref{prop_covariate}).
	The $y$-axis measures the loss of STL minus MTL.}
	\label{fig_model_shift_phasetrans}
	\vspace{-0.2in}
\end{figure}

%Concretely, we show a tight bound on the trace of $(X_1^{\top}X_1 + X_2^{\top}X_2)^{-1}$, which
%Theorem \ref{lem_cov_shift_informal} allows us to analyze the bias-variance tradeoff of the multi-task estimator for two settings:
%(i) two tasks with arbitrary covariate shift; (ii) many tasks with no covariate shift.
